Data_Spatial

### 2020-07-13 src/Data_Spatial.Rmd

#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-01-21", end = "2019-06-02")
names(Wks2019)[1:2] <- c("dateOnly", "date") #413788 obs
Wks2019$Year <- rep(2019)
Wks2020 <- selectByDate(bb2020, start = "2020-01-20", end = "2020-05-31")
names(Wks2020)[1:2] <- c("dateOnly", "date") #521773 obs
Wks2020$Year <- rep(2020)
TSbb19_20 <- rbind(Wks2019, Wks2020) #935561 obs

>>>>

#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-03-04", end = "2019-05-31")
names(Wks2019)[1:2] <- c("dateOnly", "date") #413788 obs
Wks2019$Year <- rep(2019)
Wks2020 <- selectByDate(bb2020, start = "2020-03-02", end = "2020-05-29")
names(Wks2020)[1:2] <- c("dateOnly", "date") #521773 obs
Wks2020$Year <- rep(2020)
TSbb19_20 <- rbind(Wks2019, Wks2020) #935561 obs
